Summer 2025 ToDo

### 2025-06-17 Relations/Paper/Summer_2025_TODO.tex

  \item Other ToDo
  \begin{todolist}
    \item [\done] Make Latex version of WF implications (initial draft).
    \item [\done] Verify which implications have and have not been formalized from the image.
    \item (Missing imp) $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$.
    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
    \item [\done] (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition.
    \item [\done] Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper. I need to go through it and either understand it or come with questions to Friday's meeting.
  \end{todolist}
\end{itemize}

@@

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
  \item Working on CR $\to$ CP. Low priority.
\end{todolist}

\section*{Week starting 2nd June}
\begin{todolist}
  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
  \item For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
  \item Remove "desired implications" and similar organizational issues in the code (general review)
  \item Consider defining FB in terms of existing list library; especially in the rebooted repo,
  we shouldn't use manual List type just for this.
  \item Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
  \item Revise section 3.1
\end{todolist}
\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
\begin{todolist}
  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
  \item [\done] Proof of (iii), line 296: do we really need () around SN?
  \item Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.  Hence, the tables include a separate column for their combination.
  \item  In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.  Am I missing something?). \sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses. I'm hoping that we've done enough to show to the reader how to read the table at this point. If you disagree I'm happy to add it in though. As to why have local and global counterexamples, good point. Unless either of us can think of a reason we'll remove in the next meeting.}
    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
\end{todolist}
\end{document}

>>>>

  \item Other ToDo
  \begin{todolist}
    \item [\done] Make Latex version of WF implications (initial draft).
    \item [\done] Verify which implications have and have not been formalized from the image.
    \item [\done] $\lnot \lnot$ WFacc $\leftrightarrow$ $\lnot \lnot WFind$.
    \apcomment{WFind to be removed, this is addressed in the Friday June 13th notes}
    \item [\done] (Missing imp) WFmin- $\to$ WFDNE-
    \item [\done] (Missing imp) All of the implicaions from the standard WF definition to the $\lnot \lnot$ definition.
    \item [\done] Sam TODO: I still don't have a coherent understanding in my head as to how we relate the WF and ARS sections of the paper. I need to go through it and either understand it or come with questions to Friday's meeting.
  \end{todolist}
\end{itemize}

@@

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
  \item [\done] Working on CR $\to$ CP. Low priority. \apcomment{This is mentioned as one of the research items above}
\end{todolist}

\section*{Week starting 2nd June}
\begin{todolist}
  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
  \item [\done] For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
  \item Remove "desired implications" and similar organizational issues in the code (general review)
  \item Consider defining FB in terms of existing list library; especially in the rebooted repo,
  we shouldn't use manual List type just for this.
  \item [\done] Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
  \item Revise section 3.1
\end{todolist}
\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
\begin{todolist}
  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
  \item [\done] Proof of (iii), line 296: do we really need () around SN?
  \item Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.  Hence, the tables include a separate column for their combination.
  \item  In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.  Am I missing something?). \sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses. I'm hoping that we've done enough to show to the reader how to read the table at this point. If you disagree I'm happy to add it in though. As to why have local and global counterexamples, good point. Unless either of us can think of a reason we'll remove in the next meeting.}
    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
\end{todolist}

\subsection*{Notes from meeting on Friday June 13th}

\begin{itemize}
  \item Perhaps we should not create variations and multiple implications of WFind,
  but rather prove that it's equivalent to WFacc, but lands in a higher universe.
  Mention this once at the beginning of section 5 then proceed to analyze
  connections between WFacc and WFseq/WFmin.
\end{itemize}

\end{document}
